\documentclass{article}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[
  a4paper, mag=1000,
  left=3.0cm, right=1cm, top=2cm, bottom=2cm, headsep=0.7cm, footskip=1cm
]{geometry}

\title{RRSPH v3.0.19}
\author{Asrankulov Alexander}
\date{October 2024}

\begin{document}

\maketitle

\section{Experiment}

\subsection{Experiment directory}\

Experiment directory is a directory with parameters files and particles data. 
You should provide specifically prepared directory to solver.

Minimal experiment directory to start an experiment is presented below:
\begin{verbatim}
\---experiment_00
    |   ModelParams.json
    |   ParticleParams.json
    |   
    \---dump
            0.csv
\end{verbatim}

Any RRSPH simulation program started from parent directory will produce the following output:
\begin{verbatim}
Found experiments:
[-1] Change search directory
[0] experiment_00: (0/1) data/dump layers
Type experiment id you want to load:
>
\end{verbatim}
You should type '0' and press 'Enter' in order to start simulation with specified parameters and initial state.

Experiment directories with 'ParticleParams.json' and initial state ('dump/0.csv') are usually generated with scripts. Mathematical model's 'ModelParams.json' is user-provided: manually or by SPH2DParamsGenerator app.

\subsection{RRSPH package}

\subsubsection{SPH2D simulation}\

There are two simulation programs:
\begin{itemize}
    \item SPH2D\_OMP. SPH 2D solver running on CPU with OpenMP or single-threaded.
    \item SPH2D\_CL. SPH 2D solver running on GPU with OpenCL runtime. It's executable file is distributed with CL source code in separate directory:

    \begin{verbatim}
        |   SPH2D_CL.exe
        |
        +---cl
        |       ArtificialViscosity.cl
        |       AverageVelocity.cl
        |       clErrorCodes.txt
        |       clparams.h
        |       common.h
        |       Density.cl
        |       EOS.cl
        |       ExternalForce.cl
        |       GridFind.cl
        |       GridUtils.h
        |       InternalForce.cl
        |       ParamsEnumeration.h
        |       SmoothingKernel.cl
        |       SmoothingKernel.h
        |       TimeIntegration.cl
        |   
        \---experiment_00
            |   ModelParams.json
            |   ParticleParams.json
            |   SPH2DParams.json
            |   
            \---dump
                    0.csv
    \end{verbatim}
\end{itemize}

\subsubsection{SPH2D Post-processing}

There's several post-processing programs:
\begin{itemize}
    \item WaterProfile. This app can be used to compute water profiles in space and time.
    \item FuncAtPoint. This app can be used to extract field variable at specified point in space by SPH smoothing.
    \item PartToGridConverter. This app can be used to convert SPH particles output into grid to process as mesh algorithm's output.
\end{itemize}

\section{Parameters Scheme}
\input{ModelParams.tex}
\input{ParticleParams.tex}
\input{ComputingParams.tex}
\input{LoadingParams.tex}
\input{HeightTestingParams.tex}
\end{document}
