\subsection{Particle Params}

\subsubsection{Target version}

\begin{itemize}
    \item \verb|params_target_version_major|
    \item \verb|params_target_version_minor|
    \item \verb|params_target_version_patch|
\end{itemize}

\subsubsection{Particle count}

\begin{itemize}
    \item \verb|nfluid|. Fluid particles count.
    \item \verb|nvirt|. Boundary (virtual) particles count.
    \item \verb|ntotal|. Total particles count (fluid + boundary).
\end{itemize}

\subsubsection{Geometry}
These parameters describe simulation domain area.

\begin{itemize}
    \item \verb|x_mingeom|. Left side of the domain.
    \item \verb|x_maxgeom|. Right side of the domain.
    \item \verb|y_mingeom|. Bottom of the domain.
    \item \verb|y_maxgeom|. Top of the domain.
\end{itemize}

\subsubsection{Particles parameters}

\begin{itemize}
    \item \verb|delta|. Initial distance between particles $\delta_{0}$.
    \item \verb|rho0|. Reference density of particles $\rho_{0}$.
    
    Optional parameter. Default value is $\rho_{0} = 1000$.
\end{itemize}

\subsubsection{Extra parameters}

\begin{itemize}
    \item \verb|depth|. Reference depth of the fluid $d$.
    
    Optional parameter. By default $d = \max\limits_{i}y_{i}$ on the start.
\end{itemize}

\subsubsection{Numerical Waves Maker}
If \verb|nwm| is piston or disappearing wall, affected boundary particles are from the contiguous block characterized by two indices: [start; end).

\begin{itemize}
    \item \verb|nwm_particles_start|. Index of the first particle in moving or disappearing block.
    \item \verb|nwm_particles_end|. Index of the next to the last particle in moving or disappearing block.
\end{itemize}